Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2019-10-03 manuscript.tex
Remove Geophysics formatting from the article
Make a author version for archival.

% A manuscript style format with figures included. This is one you can read.

\pdfoutput=1
\documentclass[paper,twocolumn]{geophysics}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand{\mitbf}[1]{\mathbf{{#1}}}

% To leave comments
\usepackage[colorinlistoftodos]{todonotes}

\title{
    Tesseroids: forward modeling gravitational fields in spherical coordinates
}
\author{
    Leonardo Uieda\footnotemark[1]\footnotemark[2],
    Val\'eria C. F. Barbosa\footnotemark[2],
    and
    Carla Braitenberg\footnotemark[3]
}

@@

@@

\righthead{Tesseroids: modeling in spherical coordinates}
\ms{GEO-2015-0204} % manuscript number

\address{Peer-reviewed code related to this article can be found at
http://software.seg.org/2016/0004.
\\
\footnotemark[1]Universidade do Estado do Rio de Janeiro,
Rio de Janeiro, Brazil.
email: leouieda@gmail.com
\\
\footnotemark[2]Observat\'orio Nacional,
Rio de Janeiro, Brazil.
email: valcris@on.br
\\
\footnotemark[3]Department of Mathematics and Geosciences,
University of Trieste, Trieste, Italy
}

>>>>

\documentclass[twocolumn]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

\newcommand{\mitbf}[1]{\mathbf{{#1}}}

\newcommand{\Title}{
    Tesseroids: forward modeling gravitational fields in spherical coordinates
}
\newcommand{\Author}{Uieda, L., Barbosa, V.C.F., Braitenberg, C.}
\newcommand{\AuthorAffil}{
    {\large
        Leonardo Uieda$^{1,2,*}$,
        Val\'eria C. F. Barbosa$^{2}$,
        and
        Carla Braitenberg$^{3}$
    }
    \\[0.4cm]
    {\small $^1$ Universidade do Estado do Rio de Janeiro, Rio de Janeiro, Brazil.}
    \\
    {\small $^2$ Observat\'orio Nacional, Rio de Janeiro, Brazil.}
    \\
    {\small $^3$ Department of Mathematics and Geosciences, University of Trieste, Trieste, Italy}
    \\
    {\small $^*$ e-mail: leouieda@gmail.com}
}
\newcommand{\DOI}{10.1190/geo2015-0204.1}
\newcommand{\DOILink}{\href{https://doi.org/\DOI}{doi.org/\DOI}}

\setlength{\columnsep}{2\columnsep}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author{}, 2016. \DOILink{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

\title{
}

@@

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    Accepted 2016 July 11. Received in original form 2015 March 30.
    \\[0.4cm]
    This is a pre-copyedited, author-produced PDF of an article accepted for
    publication in \textit{Geophysics} following peer review.
    The version of record
    ``\textit{\Author{} (2016). \Title{}. Geophysics. doi:\DOI{}}''
    is available online at: \DOILink{}.
}

@@

\noindent Peer-reviewed code related to this article can be found at
\href{http://software.seg.org/2016/0004}{software.seg.org/2016/0004} or
\href{https://github.com/pinga-lab/paper-tesseroids}{github.com/pinga-lab/paper-tesseroids}.
